3D MAGNETIC MODELLING FOR ELLIPSOIDS

### 2017-01-11 manuscript/Paper-magnetic-elipsoid_metodologia.tex
Metodologia Triaxial, prolato e oblato

\title{3D MAGNETIC MODELLING FOR ELIPSOIDS}

@@

@@

\subsection{The forward model of a oblate ellipsoid}

>>>>

\title{3D MAGNETIC MODELLING FOR ELLIPSOIDS}

@@

Important to remenber that all this calcuations are in the body's coordinates. In order to transform to the observations points use equation \eqref{eq:7}.

@@

\begin{equation}
\textbf{M}_i^j = \dfrac{1}{(a^2+\lambda)^{1/2}(b^2+\lambda)}
\left[\begin{matrix} 
\dfrac{\partial \lambda}{\partial x_1} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_1} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_1} \dfrac{x_3}{b^2+\lambda} \\\\
\dfrac{\partial \lambda}{\partial x_2} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_2} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_2} \dfrac{x_3}{b^2+\lambda} \\\\
\dfrac{\partial \lambda}{\partial x_3} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_3} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_3} \dfrac{x_3}{b^2+\lambda}
\end{matrix}\right]_{3 \times 3}
\end{equation}

\begin{equation}
\textbf{D}_i^j =
\left[\begin{matrix} 
A(\lambda) & 0 & 0 \\
0 & B(\lambda) & 0 \\
0 & 0 & B(\lambda)
\end{matrix}\right],
\end{equation}

where:
\begin{equation}
A(\lambda) = \dfrac{2}{(a^2-b^2)^{3/2}} \left\{\sqrt{\dfrac{a^2-b^2}{a^2+ \lambda}} - \log_e[\dfrac{(a^2-b^2)^{1/2} + (a^2+\lambda)^{1/2}}{(b^2+\lambda)^{1/2}}]  \right\}
\end{equation}

\begin{equation}
B(\lambda) = \dfrac{1}{(a^2-b^2)^{3/2}} \left\{\dfrac{\sqrt{(a^2-b^2)(a^2+\lambda)}}{b^2+\lambda} - \log_e[\dfrac{(a^2-b^2)^{1/2} + (a^2+\lambda)^{1/2}}{(b^2+\lambda)^{1/2}}]  \right\}
\end{equation}

\subsection{The forward model of an oblate ellipsoid}

The magnetic field generated by an oblate ellipsoid ($b$ > $a$), also must be calculated in the body's coordinate. The matrix $\textbf{V}$ is composed by the same equations shown for the prolate ellipsoid, but doing the changes due to the major semi-axe being $b$ :
\begin{equation}
\textbf{v}_1 = (l_1,l_2,l_3) = (\cos\alpha \sin\delta, -\cos\alpha \cos\delta, -\sin\alpha)
\end{equation}

\begin{equation}
\textbf{v}_2 = (m_1,m_2,m_3) = (\sin\alpha \sin\delta, -\sin\alpha \cos\delta, \cos\alpha)
\end{equation}

\begin{equation}
\textbf{v}_3 = (n_1,n_2,n_3) = (-\cos\delta, -\sin\delta, 0)
\end{equation}

The coordinate transformation is the same as equation \eqref{eq:bodyco}.
The calculation of $\lambda$ is and its spatial derivatives are the same as the prolate case.

The demagnetization factor are:
\begin{equation}
N_1 = \dfrac{4\pi ab^2}{(b^2-a^2)^{3/2}} \left[\dfrac{\sqrt{b^2-a^2}}{a} - \tan^{-1} \dfrac{\sqrt{b^2-a^2}}{a}\right]
\end{equation}

\begin{equation}
\textbf{M}_i^j = \dfrac{1}{(a^2+\lambda)^{1/2}(b^2+\lambda)}
\left[\begin{matrix} 
\dfrac{\partial \lambda}{\partial x_1} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_1} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_1} \dfrac{x_3}{b^2+\lambda} \\\\
\dfrac{\partial \lambda}{\partial x_2} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_2} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_2} \dfrac{x_3}{b^2+\lambda} \\\\
\dfrac{\partial \lambda}{\partial x_3} \dfrac{x_1}{a^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_3} \dfrac{x_2}{b^2+\lambda} \quad & \dfrac{\partial \lambda}{\partial x_3} \dfrac{x_3}{b^2+\lambda}
\end{matrix}\right]_{3 \times 3}
\end{equation}

\begin{equation}
\textbf{D}_i^j =
\left[\begin{matrix} 
A(\lambda) & 0 & 0 \\
0 & B(\lambda) & 0 \\
0 & 0 & B(\lambda)
\end{matrix}\right],
\end{equation}

where:
\begin{equation}
A(\lambda) = \dfrac{2}{(b^2-a^2)^{3/2}} \left\{\sqrt{\dfrac{b^2-a^2}{a^2+ \lambda}} - \tan^{-1}\sqrt{\dfrac{b^2-a^2}{a^2+\lambda}}  \right\}
\end{equation}

\begin{equation}
B(\lambda) = \dfrac{1}{(b^2-a^2)^{3/2}} \left\{\tan^{-1}\sqrt{\dfrac{b^2-a^2}{a^2+\lambda}} - \dfrac{\sqrt{(b^2-a^2)(a^2+\lambda)}}{b^2+\lambda}  \right\}
\end{equation}
